---
editor: source
editor_options: 
  chunk_output_type: console
execute: 
  echo: false
---

```{r}
#| include: false

library(tidyverse)
library(DT)

readxl::read_xlsx("backup/andic_all_merged.xlsx") |> 
  filter(!is.na(base)) |> 
  select(meaning_ru, base, gender, abs.pl, obl.sg, obl.pl, loc, GA, aor_perf, imp) |> 
  rename(russian = meaning_ru,
         zilo = base) |> 
  mutate(across(everything(), ~ str_replace_all(.x, "[1I]", "ӏ"))) |> 
  write_csv("data/data.csv", na = "")

df <- read_csv("data/data.csv", show_col_types = FALSE)

# update version everywhere
version <- "1.0.1"

read_lines("CITATION.cff") |> 
  str_replace("version: v\\d{1,}\\.\\d{1,}\\.\\d{1,}",
              str_glue("version: v{version}")) |> 
  write_lines("CITATION.cff")

read_lines("README.md") |> 
  str_replace("\\(v\\d{1,}\\.\\d{1,}\\.\\d{1,}\\)",
              str_glue("(v{version})")) |> 
  write_lines("README.md")
```


::: {.content-visible when-profile="english"}

The dictionary was compiled in 2022--2024 by G. Moroz (Linguistic Convergence Laboratory, HSE University). The online version was prepared by G. Moroz. You can always contact me via [email](mailto:agricolamz@gmail.com) or leave an issue on the [GitHub page](https://github.com/agricolamz/zilo_dictionary/issues/new). Please note that I use the [palochka sign](https://en.wikipedia.org/wiki/Palochka), however it is possible to use latin capital I or digit 1 in the colomn's search. Data are [available for download](https://raw.githubusercontent.com/LingConLab/zilo_dictionary/refs/heads/main/data/data.csv) in the `.csv` format. Dictionary consists of `r nrow(df)` lemmata.

Please refer to the dictionary as follows:

```{r}
library(RefManageR)
BibOptions(check.entries = FALSE, style = 'text', bib.style = 'authoryear')
article_citation <- BibEntry(bibtype = 'misc', 
 key='moroz2024',
 title=str_glue('Online Dictionary of Zilo Andi (v{version})'),
 author='G. Moroz',
 year='2024',
 publisher='Linguistic Convergence Laboratory, HSE University',
 address='Moscow',
 url='https://lingconlab.github.io/zilo_dictionary/',
 doi='10.5281/zenodo.13952695')
```

::: {.panel-tabset}

### Plain text

```{r, results = 'asis'}
print(article_citation, .opts = list(style = 'text'))
```

### BibTeX

```{r}
print(article_citation, .opts = list(style = 'Bibtex'))
```

:::

:::

::: {.content-visible when-profile="russian"}

Словарь был составлен в 2022--2024 Г. А. Морозом (Международная лаборатория языковой конвергенции, НИУ ВШЭ). Сайт сверстан Г. А. Морозом. По всем вопросам можно написать [по почте](mailto:agricolamz@gmail.com) или оставить замечания на [странице GitHub](https://github.com/agricolamz/zilo_dictionary/issues/new). Обратите внимание, что я использую [палочку](https://ru.wikipedia.org/wiki/Палочка_(кириллица))), но в поиске конкретных колонок можно использовать заглавную английскую I или цифру 1. Данные доступны  [к скачиванию](https://raw.githubusercontent.com/LingConLab/zilo_dictionary/refs/heads/main/data/data.csv) в формате `.csv`. В словаре содержится `r nrow(df)` лемм.

Словарь следует цитировать следующим образом:

```{r}
library(RefManageR)
BibOptions(check.entries = FALSE, style = 'text', bib.style = 'authoryear')
article_citation <- BibEntry(bibtype = 'misc', 
 key='moroz2024',
 title=str_glue('Электронный словарь зиловского андийского (v{version})'),
 author='Г. А. Мороз',
 year='2024',
 publisher='Международная лаборатория языковой конвергенции, НИУ ВШЭ',
 address='Москва',
 url='https://agricolamz.github.io/zilo_dictionary',
 doi='10.5281/zenodo.7803955')
```

::: {.panel-tabset}

### Plain text

```{r, results = 'asis'}
print(article_citation, .opts = list(style = 'text'))
```

### BibTeX

```{r}
print(article_citation, .opts = list(style = 'Bibtex'))
```

:::

:::

[![](https://zenodo.org/badge/DOI/10.5281/zenodo.13952696.svg)](https://doi.org/10.5281/zenodo.13952695)

```{r}
#| warning: false

df |> 
  arrange(zilo) |> 
  mutate_all(function(i){ifelse(is.na(i), "", i)}) |>
  mutate(gender = factor(gender)) |> 
  datatable(filter = 'top', escape = FALSE, rownames = FALSE,
            options = list(pageLength = 20, 
                           dom = 'ftop',
                           initComplete = JS(readLines("character_map.js"))))
```

